Median Maximum Pairwise Distance

### 2020-09-30 main.Rmd
adding CLT, EVT and simulations
distribution of median and sd added

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
read_chunk('main.R')
read_chunk("null_distribution.R")
```

@@

When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider. To be able to dice time in all possible ways in order to have multiple perspectives about peridicities in the data, there are too many things that we should look at ideally. Exploratory analysis is detective work and it is difficult to traverse through all possible ways without any systematic approach. It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation. The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data. Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption. Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies for further exploration/visualization. Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data. Here, we have two main objectives:

@@

@@

@@

>>>>

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
read_chunk('main.R')
read_chunk("null_distribution.R")
read_chunk("mean_null.R")
```

@@

When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider. In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months. But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions. The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data. Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption. Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies for further exploration/visualization. Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data. Here, we have two main objectives:

@@

To be able to dice time in all possible ways in order to have multiple perspectives about peridicities in the data, there are too many things that we should look at ideally. Exploratory analysis is detective work and it is difficult to traverse through all possible ways without any systematic approach. It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation.

Talk about Scagnostics: Tukey

@@

### why normalize

Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let 
$Y = max(X_1, X_2, \dots, X_n)$.

Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using:
$F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$. For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$. But what about the case when $n$ is not large enough? The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $X$. If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$. Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then
$f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$. Hence, we are trying to normalise for $n$. Also, it depends on the underlying distribution of $X$, which we have assumed as normal in our case. As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more. Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution. But in our case, we will mostly have small $n$. It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$. We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.

```{r create_simdata}

```{r create_nlevels}

```{r norm_max_new}

## Mean and standard deviation of the distribution of maximum

```{r}
library(ggridges)
library(viridis)
max_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
                           nsim = 500,
                           sim_dist = distributional::dist_normal(5, 10), create_fun = max)

g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max")

median_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
                           nsim = 500,
                           sim_dist = distributional::dist_normal(5, 10), create_fun = median)

g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median")

ggpubr::ggarrange(g1, g2, ncol = 2)

@@

### Confidence interval of test statistic
